High frequency intraday forex rates forecasting using an online cointegration approach

### 2015-06-30 manuscript/manuscript.tex
adding statistics table

Finally, the three settings are compared with OOVECM. We can see that RR and AAR approaches are better than traditional OLS and also AAR seems to perform better than RR.

@@

>>>>

The three settings are compared with OOVECM. We can see that RR and AAR approaches are better than traditional OLS and also AAR seems to perform better than RR.

@@

Additionally table \ref{tab:stats} shows the MAPE, MAE and RMSE statistics. This results also shows that AAR behaves better than RR and OLS in comparison to OOVECM.

\begin{table*}[ht!]
\caption{Model measures}
\label{tab:stats}
\begin{center}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\hline
Method & $Solver$  & $\lambda$ & 
MAPE & MAE& RMSE \\
\hline
 OVECM  &   OLS   &  0.0&  0.00189&  1.169e-05&3.955e-05\\
 OVECM  &   RR   & 0.00 &  0.00142& 9.167e-06 &1.713e-05\\
 OVECM  &   AAR     &  1e-06 &  0.00115&  7.605e-06&1.197e-05\\
 OOVECM  &   OLS    &  1e-06 &  0.00103&  6.880e-06&1.148e-05\\
\hline
\end{tabular}
\end{center}
\end{table*}
